---
title: "March Madness 2026"
author: "Andrew Stomper"
date: "2026-03-19"
output:
  # html_document:
    # toc: true
    # toc_float: true
    # toc_collapsed: true
    # toc_depth: 3
    # number_sections: true
    rmdformats::readthedown
editor_options: 
  markdown: 
    wrap: 72
---

<style type="text/css">
.main-container {
  max-width: 100% !important;
  margin: auto;
}
</style>

```{r libraries, echo=FALSE, include=FALSE}
library(ggplot2)
library(data.table)
library(magrittr)
library(DT)
library(knitr)
library(webshot)
library(DBI)
library(htmltools)
library(flextable)
library(lubridate)
library(scales)
library(rmdformats)
library(dplyr)
library(ggplot2)
options(width = 180) 

knitr::opts_chunk$set(warning = FALSE, message = FALSE) 

```

# Introduction {#Introduction}

The goal of this model is to maximize your chances of winning your March Madness Bracket. 

The purpose of this exercise is not necessarily to build the bracket with the highest
expected value but rather to consider both the *true* probability of teams winning 
and the popularity of other players in your group to pick those teams. The best brackets
are not the ones that pick the teams that are most likely to win; it is the brackets
that pick winners that are likely to win *and* are not picked in your competitors brackets.

The optimal winners very based on group size. For a small group, the favorites may be good; however, 
for very large groups (N > 250), more upsets help your chances at winning. **In no way am I guaranteeing a win, simply just increasing the chances of doing so.**

In this years tournament #1 seeds are stronger than ever. Most of them as likely to make the 
final four as not. As expected, favorites are popular among the public, but with especially strong
one seeds, for most group sizes (N < 60), *chalk* may be the best approach this year. 

<!-- maybe change -->
In almost every bracket size the ideal winner is **Houston**. The Cougars have a 15.4% chance 
to win the tournament but only 8.6% of Yahoo users are picking them. 


The following will walk through the process and results of the model for different group sizes. 

# Data {#Data}

There are two main sets of data. The *expected* data and the *popular* data. A few sources were considered 
for the *expected* mainly the implied probability from sportsbooks. This can be done by converting the betting odds into a proability and de-vigging (removing the house edge) the odds for each team to make a certain round. The issue with this data is that the amount of vig may not be the same in each line (e.g. a longshot may have more vig as it represents a larger risk to the sportsbook). Additionally, getting this data is manual and tedious. This year, I made some manual adjustments to the odds for very high seeds (>13) to win it all in 
order for the final implied probabilities to make sense.

For the popular pick data, until 2023, ESPN would offer *Who Picked Whom* data, but unfortunatley Disney had to kill it. CBS also offers it, but in the most
immpossibly tedious way - you have to fill out a hypothetical bracket and it will tell you each teams
popularity to go to the next round. Luckily Yahoo still offers the public free popularity data.

Of course, the implicit assumption is that the competitors in your group pick like
the average user at Yahoo. On the fringes that is unlikely. I would hope no one is picking 14-seed
UPenn to win it all like 0.2% of Yahoo users. 

The data is structured as the probability that each team makes it to each round. 
For example, *Final Four* for Duke means that Duke has a 48.5% chance to *at least* make
the final four while 64.2% of Yahoo users are picking them to make it.

The data is admittedly outdated, it was pulled 3/17, so these numbers have changed slighlty
for the popular pick. In my opinion, the numbers did not change enough to materially affect
results. 

Below is the popular data compared to expected data, by round. 

## Comparison of Data {.tabset}

### Champion

```{r data1, echo=FALSE, include=TRUE}

expected <- fread("data/dk_26.csv")
popular <- fread("data/yahoo_wpw.csv")

output_1 <- expected[, .(Seed, Team, Expected = six)][popular, Popular := i.six, on = .(Team)][order(Expected, decreasing = TRUE)][, `Value Over Popular` := Expected - Popular]

DT::datatable(
  output_1, 
  filter = "top",
  # options = list(
  #   columnDefs = list(
  #     list(targets = 3, render = render)
  #   )
  # )
)  %>% 
  formatPercentage(c("Expected", "Popular", "Value Over Popular"), digits = 1)

```

### Make Championship

Probability to make the championship - Win or Lose

```{r data2, echo=FALSE, include=TRUE}

expected <- fread("data/dk_26.csv")
popular <- fread("data/yahoo_wpw.csv")

output_2 <- expected[, .(Seed, Team, Expected = five)][popular, Popular := i.five, on = .(Team)][order(Expected, decreasing = TRUE)][, `Value Over Popular` := Expected - Popular]

DT::datatable(
  output_2, 
  filter = "top",
  # options = list(
  #   columnDefs = list(
  #     list(targets = 3, render = render)
  #   )
  # )
)  %>% 
  formatPercentage(c("Expected", "Popular", "Value Over Popular"), digits = 1)

```

### Final Four
```{r data3, echo=FALSE, include=TRUE}

expected <- fread("data/dk_26.csv")
popular <- fread("data/yahoo_wpw.csv")

output_3 <- expected[, .(Seed, Team, Expected = four)][popular, Popular := i.four, on = .(Team)][order(Expected, decreasing = TRUE)][, `Value Over Popular` := Expected - Popular]

DT::datatable(
  output_3, 
  filter = "top",
  # options = list(
  #   columnDefs = list(
  #     list(targets = 3, render = render)
  #   )
  # )
)  %>% 
  formatPercentage(c("Expected", "Popular", "Value Over Popular"), digits = 1)

```

### Elite Eight
```{r data4, echo=FALSE, include=TRUE}

expected <- fread("data/dk_26.csv")
popular <- fread("data/yahoo_wpw.csv")

output_4 <- expected[, .(Seed, Team, Expected = three)][popular, Popular := i.three, on = .(Team)][order(Expected, decreasing = TRUE)][, `Value Over Popular` := Expected - Popular]

DT::datatable(
  output_4, 
  filter = "top",
  # options = list(
  #   columnDefs = list(
  #     list(targets = 3, render = render)
  #   )
  # )
)  %>%  
  formatPercentage(c("Expected", "Popular", "Value Over Popular"), digits = 1)

```

### Sweet Sixteen
```{r data5, echo=FALSE, include=TRUE}

expected <- fread("data/dk_26.csv")
popular <- fread("data/yahoo_wpw.csv")

output_5 <- expected[, .(Seed, Team, Expected = two)][popular, Popular := i.two, on = .(Team)][order(Expected, decreasing = TRUE)][, `Value Over Popular` := Expected - Popular]

DT::datatable(
  output_5, 
  filter = "top",
  # options = list(
  #   columnDefs = list(
  #     list(targets = 3, render = render)
  #   )
  # )
)  %>% 
  formatPercentage(c("Expected", "Popular", "Value Over Popular"), digits = 1)

```

# Process {#Process}

Given the unimaginable amount of bracket combinations, a simulation, rather than discrete, approach is used.

First a set of 10,000 outcomes is simulated using the expected probabilities of each 
team to make it to each round. Next, a group of size N, is simulated for each of those 10,000 
simualtions. The distribution of the group brackets is based on the popular pick data.
The brackets in those groups are graded and the necessary amount of points to win is determined. 

Next, 1,000 brackets are created sampling from the expected probabilities. They are graded
based on each of the 10,000 outcomes/groups and we see how many each bracket wins. 

The top 25% of brackets are determined. The sampling for the next 1,000 testing brackets
will be sampled from a weighted distribution of the initial expected probabilities and the distribution of the best brackets from the prior iteration. This a process known as **Genetic Sampling**. I used 20 iterations, but in the N=20 example, the model 
converged (one bracket won 3 times in a row) after 7 iterations.

The top 5% of brackets are rolled over to the next round of simulation to test against a new set of outcomes. 

The next round of simulation begins by creating 10,000 new outcomes. The groups are 
preserved to save computing power, but they are regraded on the new outcomes. 


# Results (Group Size = 20)

For a relativley small group of 20 the optimal bracket is quite chalky. As mentioned in the Intro, Houston is the optimal winner in basically any size bracket that I have the ability to simulate. 

The expected value of a random bracket in a 20 person pool is 5%. Using this bracket the expected win percentage is ~12%. That means for a $20 buy your expected winnings increases from $0 to $28! That should hopefully cover the $5 I had to pay to Evan Miya for the data. 

Also, yes, the names on the brackets get cut off and are abbreviated weirdly. Consider that on the list of improvements for 2026.

```{r results_20, echo=FALSE, include=TRUE, R.options = list(width = 240)}

best_bracket <- fread('outputs/best_bracket_20.csv')

first_evens <- function(x) {seq(from=2,to=2*x,length.out=x)}
first_odds <- function(x) {seq(from=1,to=2*x-1,length.out=x)}

### calculate y-values for horizontal lines:
### this is for top-left corner of the bracket,
### but multiplying sequences by -1 makes these 
### values work for bottom right and left corners;
### final round has teams at y=2*off.set

r1.y.width <- 1.5*strheight(s="Virginia Common",units="in") # this effects the width of the first round
r1.y.offset <- 0.125*r1.y.width # this effects distance from y=0

r1.y <- seq(from=r1.y.offset,to=r1.y.offset+r1.y.width,length.out=16)
r2.y <- seq(from=mean(r1.y[1:2]),to=mean(r1.y[15:16]),length.out=8)
r3.y <- seq(from=mean(r2.y[1:2]),to=mean(r2.y[7:8]),length.out=4)
r4.y <- seq(from=mean(r3.y[1:2]),to=mean(r3.y[3:4]),length.out=2)
r5.y <- seq(from=mean(r4.y[1:2]),to=mean(r4.y[1:2]),length.out=1)
r6.y <- 1.5*r1.y.offset

### calculate horizontal bar start and stop coordinates
### note that there are 6 total rounds -- 5 rounds per quadrant
r1.x.width <- 1.25*strwidth("Viriginia Commonwealth","inches") # how long should horizontal lines be?
r1.x.offset <- 1
round.break.points <- -(seq(from=0,to=7*r1.x.width,by=r1.x.width)+r1.x.offset)

r1.x <- round.break.points[7:6]
r2.x <- round.break.points[6:5]
r3.x <- round.break.points[5:4]
r4.x <- round.break.points[4:3]
r5.x <- round.break.points[3:2]
r6.x <- round.break.points[2:1]

### calculate verticals line coordinates: these are based off of
### r1.y values. Round 5 verticals need to connect the four subtrees
### via the top-left <-> bottom-left and top-right <-> bottom-right

r1.verticals.start <- r1.y[first_odds(8)]
r1.verticals.stop <- r1.y[first_evens(8)]

r2.verticals.start <- r2.y[first_odds(4)]
r2.verticals.stop <- r2.y[first_evens(4)]

r3.verticals.start <- r3.y[first_odds(2)]
r3.verticals.stop <- r3.y[first_evens(2)]

r4.verticals.start <- r4.y[first_odds(1)]
r4.verticals.stop <- r4.y[first_evens(1)]

r5.verticals.start <- r5.y[1]
r5.verticals.stop <- -r5.y[1]

empty.bracket <- ggplot() + theme_bw() + theme(axis.line=element_blank(), axis.text.x=element_blank(), axis.text.y=element_blank(), axis.ticks=element_blank(), axis.title.x=element_blank(), axis.title.y=element_blank(), panel.border=element_blank(), panel.grid.major.x=element_blank(), panel.grid.minor.x=element_blank(), panel.grid.major.y=element_blank(), panel.grid.minor.y=element_blank(), plot.margin=unit(c(0,0,-6,-6),"mm"), text=element_text(size=12,hjust=0,vjust=0)) + coord_cartesian(ylim = c(-1.05*r1.y[16],1.05*r1.y[16]), xlim = c(1.025*r1.x[1],-1.025*r1.x[1]))

### add first round bars, and vertical connectors, make addition of each quadrant verbose
empty.bracket <- empty.bracket + geom_segment(aes(x=r1.x[1],y=r1.y,yend=r1.y,xend=r1.x[2])) + geom_segment(aes(x=r1.x[2],xend=r1.x[2],y=r1.verticals.start,yend=r1.verticals.stop)) + geom_segment(aes(x=r1.x[1],y=-r1.y,yend=-r1.y,xend=r1.x[2])) + geom_segment(aes(x=r1.x[2],xend=r1.x[2],y=-r1.verticals.start,yend=-r1.verticals.stop)) + geom_segment(aes(x=-r1.x[1],y=r1.y,yend=r1.y,xend=-r1.x[2])) + geom_segment(aes(x=-r1.x[2],xend=-r1.x[2],y=r1.verticals.start,yend=r1.verticals.stop)) + geom_segment(aes(x=-r1.x[1],y=-r1.y,yend=-r1.y,xend=-r1.x[2])) + geom_segment(aes(x=-r1.x[2],xend=-r1.x[2],y=-r1.verticals.start,yend=-r1.verticals.stop)) 

### add second round
empty.bracket <- empty.bracket + geom_segment(aes(x=r2.x[1],y=r2.y,yend=r2.y,xend=r2.x[2])) + geom_segment(aes(x=r2.x[2],xend=r2.x[2],y=r2.verticals.start,yend=r2.verticals.stop)) + geom_segment(aes(x=r2.x[1],y=-r2.y,yend=-r2.y,xend=r2.x[2])) + geom_segment(aes(x=r2.x[2],xend=r2.x[2],y=-r2.verticals.start,yend=-r2.verticals.stop)) + geom_segment(aes(x=-r2.x[1],y=r2.y,yend=r2.y,xend=-r2.x[2])) + geom_segment(aes(x=-r2.x[2],xend=-r2.x[2],y=r2.verticals.start,yend=r2.verticals.stop)) + geom_segment(aes(x=-r2.x[1],y=-r2.y,yend=-r2.y,xend=-r2.x[2])) + geom_segment(aes(x=-r2.x[2],xend=-r2.x[2],y=-r2.verticals.start,yend=-r2.verticals.stop)) 

### add third round
empty.bracket <- empty.bracket + geom_segment(aes(x=r3.x[1],y=r3.y,yend=r3.y,xend=r3.x[2])) + geom_segment(aes(x=r3.x[2],xend=r3.x[2],y=r3.verticals.start,yend=r3.verticals.stop)) + geom_segment(aes(x=r3.x[1],y=-r3.y,yend=-r3.y,xend=r3.x[2])) + geom_segment(aes(x=r3.x[2],xend=r3.x[2],y=-r3.verticals.start,yend=-r3.verticals.stop)) + geom_segment(aes(x=-r3.x[1],y=r3.y,yend=r3.y,xend=-r3.x[2])) + geom_segment(aes(x=-r3.x[2],xend=-r3.x[2],y=r3.verticals.start,yend=r3.verticals.stop)) + geom_segment(aes(x=-r3.x[1],y=-r3.y,yend=-r3.y,xend=-r3.x[2])) + geom_segment(aes(x=-r3.x[2],xend=-r3.x[2],y=-r3.verticals.start,yend=-r3.verticals.stop)) 

### add fourth round
empty.bracket <- empty.bracket + geom_segment(aes(x=r4.x[1],y=r4.y,yend=r4.y,xend=r4.x[2])) + geom_segment(aes(x=r4.x[2],xend=r4.x[2],y=r4.verticals.start,yend=r4.verticals.stop)) + geom_segment(aes(x=r4.x[1],y=-r4.y,yend=-r4.y,xend=r4.x[2])) + geom_segment(aes(x=r4.x[2],xend=r4.x[2],y=-r4.verticals.start,yend=-r4.verticals.stop)) + geom_segment(aes(x=-r4.x[1],y=r4.y,yend=r4.y,xend=-r4.x[2])) + geom_segment(aes(x=-r4.x[2],xend=-r4.x[2],y=r4.verticals.start,yend=r4.verticals.stop)) + geom_segment(aes(x=-r4.x[1],y=-r4.y,yend=-r4.y,xend=-r4.x[2])) + geom_segment(aes(x=-r4.x[2],xend=-r4.x[2],y=-r4.verticals.start,yend=-r4.verticals.stop)) 

### add fifth round: add necessary horizontal bars and then
### vertical bars
empty.bracket <- empty.bracket + geom_segment(aes(x=r5.x[1],y=r5.y,yend=r5.y,xend=r5.x[2])) +  geom_segment(aes(x=r5.x[1],y=-r5.y,yend=-r5.y,xend=r5.x[2])) + geom_segment(aes(x=r5.x[2],y=-r5.y, yend=r5.y, xend=r5.x[2])) + geom_segment(aes(x=-r5.x[1],y=r5.y,yend=r5.y,xend=-r5.x[2])) + geom_segment(aes(x=-r5.x[1],y=-r5.y,yend=-r5.y,xend=-r5.x[2])) + geom_segment(aes(x=-r5.x[2],y=-r5.y,yend=r5.y,xend=-r5.x[2])) 

### due to symmetry, the 6th (and final round)
empty.bracket <- empty.bracket  + geom_segment(aes(x=r6.x[1],y=r6.y,xend=r6.x[2],yend=r6.y)) + geom_segment(aes(x=-r6.x[1],y=-r6.y,xend=-r6.x[2],yend=-r6.y))

### add winner location
empty.bracket <- empty.bracket + geom_segment(aes(x=mean(r6.x),xend=-mean(r6.x),y=0,yend=0))

### put some test labels on the bracket slots
Labels_og <- c("Duke",
               "Siena",
               "OSU",
               "TCU",
               "St John's",
               "Northern Iowa",
               "Kansas",
               "CA Baptist",
               "Louisville",
               "USF",
               "MSU",
               "NDSU",
               "UCLA",
               "UCF",
               "UConn",
               "Furman"
)
Labels <- Labels_og
vec <- best_bracket[round == 1 & grp %like% 'E', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])
vec <- best_bracket[round == 2 & grp %like% 'E', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])
vec <- best_bracket[round == 3 & grp %like% 'E', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])
vec <- best_bracket[round == 4 & grp %like% 'E', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])



TextFrame <- data.frame(X = c(rep(r1.x[1], 16), rep(r2.x[1], 8), rep(r3.x[1], 4), rep(r4.x[1], 2), rep(r5.x[1], 1)), Y = c(rev(r1.y), rev(r2.y), rev(r3.y), rev(r4.y), rev(r5.y)), LAB = Labels)
TextFrame <- transform(TextFrame, w = strwidth(LAB, 'inches') + 0.05, h = strheight(LAB, 'inches') + 0.5)

### display results
filled_bracket <- empty.bracket + geom_rect(data = TextFrame, aes(xmin = X, xmax = X + w, ymin = Y, ymax = Y + h),alpha=0) + geom_text(data=TextFrame,aes(x=X,y=Y,label=LAB),size=rel(3),hjust=-.05,vjust=-.2)

### put some test labels on the bracket slots
Labels_og <- c("Florida",
               "Lehigh/PV",
               "Clemson",
               "Iowa",
               "Vandy",
               "McNeese",
               "Nebraska",
               "Troy",
               "UNC",
               "VCU",
               "Illinois",
               "Penn",
               "St Mary's",
               "TAMU",
               "Houston",
               'Idaho'
)
Labels <- Labels_og
vec <- best_bracket[round == 1 & grp %like% 'S', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])
vec <- best_bracket[round == 2 & grp %like% 'S', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])
vec <- best_bracket[round == 3 & grp %like% 'S', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])
vec <- best_bracket[round == 4 & grp %like% 'S', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])

TextFrame <- data.frame(X = c(rep(r1.x[1], 16), rep(r2.x[1], 8), rep(r3.x[1], 4), rep(r4.x[1], 2), rep(r5.x[1], 1)), Y = -c(r1.y, r2.y, r3.y, r4.y, r5.y), LAB = Labels)
TextFrame <- transform(TextFrame, w = strwidth(LAB, 'inches') + 0.05, h = strheight(LAB, 'inches') + 0.5)

### display results
filled_bracket <- filled_bracket + geom_rect(data = TextFrame, aes(xmin = X, xmax = X + w, ymin = Y, ymax = Y + h),alpha=0) + geom_text(data=TextFrame,aes(x=X,y=Y,label=LAB),size=rel(3),hjust=-.05,vjust=-.2)


#Top Left

### put some test labels on the bracket slots
Labels_og <- c("Arizona",
               "Long Island",
               "Villanova",
               "Utah St",
               "Wisco",
               "High Point",
               "Arkansas",
               "Hawaii",
               "BYU",
               "Texas",
               "Gonzaga",
               "Kenn St",
               "Miami FL",
               "Missouri",
               "Purdue",
               "Queens"
               
)
Labels <- Labels_og
vec <- best_bracket[round == 1 & grp %like% 'W', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])
vec <- best_bracket[round == 2 & grp %like% 'W', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])
vec <- best_bracket[round == 3 & grp %like% 'W', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])
vec <- best_bracket[round == 4 & grp %like% 'W', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])

TextFrame <- data.frame(X = -c(rep(r1.x[2], 16), rep(r2.x[2], 8), rep(r3.x[2], 4), rep(r4.x[2], 2), rep(r5.x[2], 1)), Y = c(rev(r1.y), rev(r2.y), rev(r3.y), rev(r4.y), rev(r5.y)), LAB = Labels)
TextFrame <- transform(TextFrame, w = strwidth(LAB, 'inches') + 0.05, h = strheight(LAB, 'inches') + 0.5)

### display results
filled_bracket <- filled_bracket + geom_rect(data = TextFrame, aes(xmin = X, xmax = X + w, ymin = Y, ymax = Y + h),alpha=0) + geom_text(data=TextFrame,aes(x=X,y=Y,label=LAB),size=rel(3),hjust=0,vjust=-.2)

#Bottom Right

### put some test labels on the bracket slots
Labels_og <- c("Michigan",
               "Howard",
               "Georgia",
               "SLU",
               "TTU",
               "Akron",
               "Alabama",
               "Hofstra",
               "Tennessee",
               "SMU/Miami OH",
               "Virginia",
               "Wright St",
               "Kentucky",
               "Santa Clara",
               "Iowa St",
               'Tenn St'
               
               
)
Labels <- Labels_og
vec <- best_bracket[round == 1 & grp %like% 'M', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])
vec <- best_bracket[round == 2 & grp %like% 'M', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])
vec <- best_bracket[round == 3 & grp %like% 'M', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])
vec <- best_bracket[round == 4 & grp %like% 'M', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])

TextFrame <- data.frame(X = -c(rep(r1.x[2], 16), rep(r2.x[2], 8), rep(r3.x[2], 4), rep(r4.x[2], 2), rep(r5.x[2], 1)), Y = -c(r1.y, r2.y, r3.y, r4.y, r5.y), LAB = Labels)
TextFrame <- transform(TextFrame, w = strwidth(LAB, 'inches') + 0.05, h = strheight(LAB, 'inches') + 0.5)

### display results
filled_bracket <- filled_bracket + geom_rect(data = TextFrame, aes(xmin = X, xmax = X + w, ymin = Y, ymax = Y + h),alpha=0) + geom_text(data=TextFrame,aes(x=X,y=Y,label=LAB),size=rel(3),hjust=0,vjust=-.2)


#Left Semi
semi_1 <- best_bracket[round == 5 & grp == 1, Team]

TextFrame <- data.frame(X = r6.x[1], Y = r6.y, LAB = semi_1)
TextFrame <- transform(TextFrame, w = strwidth(LAB, 'inches') + 0.05, h = strheight(LAB, 'inches') + 0.5)

### display results
filled_bracket <- filled_bracket + geom_rect(data = TextFrame, aes(xmin = X, xmax = X + w, ymin = Y, ymax = Y + h),alpha=0) + geom_text(data=TextFrame,aes(x=X,y=Y,label=LAB),size=rel(3),hjust=0,vjust=-.2)

#Right Semi
semi_2 <- best_bracket[round == 5 & grp == 2, Team]

TextFrame <- data.frame(X = -r6.x[2], Y = -r6.y, LAB = semi_2)
TextFrame <- transform(TextFrame, w = strwidth(LAB, 'inches') + 0.05, h = strheight(LAB, 'inches') + 0.5)

### display results
filled_bracket <- filled_bracket + geom_rect(data = TextFrame, aes(xmin = X, xmax = X + w, ymin = Y, ymax = Y + h),alpha=0) + geom_text(data=TextFrame,aes(x=X,y=Y,label=LAB),size=rel(3),hjust=0,vjust=-.2)

#Final
champ <- best_bracket[round == 6, Team]

TextFrame <- data.frame(X = 0, Y = 0, LAB = champ)
TextFrame <- transform(TextFrame, w = strwidth(LAB, 'inches') + 0.05, h = strheight(LAB, 'inches') + 0.5)

### display results
filled_bracket <- filled_bracket + geom_rect(data = TextFrame, aes(xmin = X, xmax = X + w, ymin = Y, ymax = Y + h),alpha=0) + geom_text(data=TextFrame,aes(x=X,y=Y,label=LAB),size=rel(3),hjust=0.5,vjust=-.2)

filled_bracket

```

# Results (Group Size = 50)

For a slightly larger group the results would still be considered chalky. However, we finally have two upsets in the Elite Eight and 
a non-one seed to the Final Four. Strangely, some of the upsets from the 20 person bracket did not make it to the 550 person bracket like VCU to the Sweet Sixteen.

The expected value of a random bracket is 1.3%. Using this bracket it is 4.8%. For a $20 buy in the expected value goes from $0 to $52.

```{r results_60, echo=FALSE, include=TRUE, R.options = list(width = 240)}

best_bracket <- fread('outputs/best_bracket_50.csv')

first_evens <- function(x) {seq(from=2,to=2*x,length.out=x)}
first_odds <- function(x) {seq(from=1,to=2*x-1,length.out=x)}

### calculate y-values for horizontal lines:
### this is for top-left corner of the bracket,
### but multiplying sequences by -1 makes these 
### values work for bottom right and left corners;
### final round has teams at y=2*off.set

r1.y.width <- 1.5*strheight(s="Virginia Common",units="in") # this effects the width of the first round
r1.y.offset <- 0.125*r1.y.width # this effects distance from y=0

r1.y <- seq(from=r1.y.offset,to=r1.y.offset+r1.y.width,length.out=16)
r2.y <- seq(from=mean(r1.y[1:2]),to=mean(r1.y[15:16]),length.out=8)
r3.y <- seq(from=mean(r2.y[1:2]),to=mean(r2.y[7:8]),length.out=4)
r4.y <- seq(from=mean(r3.y[1:2]),to=mean(r3.y[3:4]),length.out=2)
r5.y <- seq(from=mean(r4.y[1:2]),to=mean(r4.y[1:2]),length.out=1)
r6.y <- 1.5*r1.y.offset

### calculate horizontal bar start and stop coordinates
### note that there are 6 total rounds -- 5 rounds per quadrant
r1.x.width <- 1.25*strwidth("Viriginia Commonwealth","inches") # how long should horizontal lines be?
r1.x.offset <- 1
round.break.points <- -(seq(from=0,to=7*r1.x.width,by=r1.x.width)+r1.x.offset)

r1.x <- round.break.points[7:6]
r2.x <- round.break.points[6:5]
r3.x <- round.break.points[5:4]
r4.x <- round.break.points[4:3]
r5.x <- round.break.points[3:2]
r6.x <- round.break.points[2:1]

### calculate verticals line coordinates: these are based off of
### r1.y values. Round 5 verticals need to connect the four subtrees
### via the top-left <-> bottom-left and top-right <-> bottom-right

r1.verticals.start <- r1.y[first_odds(8)]
r1.verticals.stop <- r1.y[first_evens(8)]

r2.verticals.start <- r2.y[first_odds(4)]
r2.verticals.stop <- r2.y[first_evens(4)]

r3.verticals.start <- r3.y[first_odds(2)]
r3.verticals.stop <- r3.y[first_evens(2)]

r4.verticals.start <- r4.y[first_odds(1)]
r4.verticals.stop <- r4.y[first_evens(1)]

r5.verticals.start <- r5.y[1]
r5.verticals.stop <- -r5.y[1]

empty.bracket <- ggplot() + theme_bw() + theme(axis.line=element_blank(), axis.text.x=element_blank(), axis.text.y=element_blank(), axis.ticks=element_blank(), axis.title.x=element_blank(), axis.title.y=element_blank(), panel.border=element_blank(), panel.grid.major.x=element_blank(), panel.grid.minor.x=element_blank(), panel.grid.major.y=element_blank(), panel.grid.minor.y=element_blank(), plot.margin=unit(c(0,0,-6,-6),"mm"), text=element_text(size=12,hjust=0,vjust=0)) + coord_cartesian(ylim = c(-1.05*r1.y[16],1.05*r1.y[16]), xlim = c(1.025*r1.x[1],-1.025*r1.x[1]))

### add first round bars, and vertical connectors, make addition of each quadrant verbose
empty.bracket <- empty.bracket + geom_segment(aes(x=r1.x[1],y=r1.y,yend=r1.y,xend=r1.x[2])) + geom_segment(aes(x=r1.x[2],xend=r1.x[2],y=r1.verticals.start,yend=r1.verticals.stop)) + geom_segment(aes(x=r1.x[1],y=-r1.y,yend=-r1.y,xend=r1.x[2])) + geom_segment(aes(x=r1.x[2],xend=r1.x[2],y=-r1.verticals.start,yend=-r1.verticals.stop)) + geom_segment(aes(x=-r1.x[1],y=r1.y,yend=r1.y,xend=-r1.x[2])) + geom_segment(aes(x=-r1.x[2],xend=-r1.x[2],y=r1.verticals.start,yend=r1.verticals.stop)) + geom_segment(aes(x=-r1.x[1],y=-r1.y,yend=-r1.y,xend=-r1.x[2])) + geom_segment(aes(x=-r1.x[2],xend=-r1.x[2],y=-r1.verticals.start,yend=-r1.verticals.stop)) 

### add second round
empty.bracket <- empty.bracket + geom_segment(aes(x=r2.x[1],y=r2.y,yend=r2.y,xend=r2.x[2])) + geom_segment(aes(x=r2.x[2],xend=r2.x[2],y=r2.verticals.start,yend=r2.verticals.stop)) + geom_segment(aes(x=r2.x[1],y=-r2.y,yend=-r2.y,xend=r2.x[2])) + geom_segment(aes(x=r2.x[2],xend=r2.x[2],y=-r2.verticals.start,yend=-r2.verticals.stop)) + geom_segment(aes(x=-r2.x[1],y=r2.y,yend=r2.y,xend=-r2.x[2])) + geom_segment(aes(x=-r2.x[2],xend=-r2.x[2],y=r2.verticals.start,yend=r2.verticals.stop)) + geom_segment(aes(x=-r2.x[1],y=-r2.y,yend=-r2.y,xend=-r2.x[2])) + geom_segment(aes(x=-r2.x[2],xend=-r2.x[2],y=-r2.verticals.start,yend=-r2.verticals.stop)) 

### add third round
empty.bracket <- empty.bracket + geom_segment(aes(x=r3.x[1],y=r3.y,yend=r3.y,xend=r3.x[2])) + geom_segment(aes(x=r3.x[2],xend=r3.x[2],y=r3.verticals.start,yend=r3.verticals.stop)) + geom_segment(aes(x=r3.x[1],y=-r3.y,yend=-r3.y,xend=r3.x[2])) + geom_segment(aes(x=r3.x[2],xend=r3.x[2],y=-r3.verticals.start,yend=-r3.verticals.stop)) + geom_segment(aes(x=-r3.x[1],y=r3.y,yend=r3.y,xend=-r3.x[2])) + geom_segment(aes(x=-r3.x[2],xend=-r3.x[2],y=r3.verticals.start,yend=r3.verticals.stop)) + geom_segment(aes(x=-r3.x[1],y=-r3.y,yend=-r3.y,xend=-r3.x[2])) + geom_segment(aes(x=-r3.x[2],xend=-r3.x[2],y=-r3.verticals.start,yend=-r3.verticals.stop)) 

### add fourth round
empty.bracket <- empty.bracket + geom_segment(aes(x=r4.x[1],y=r4.y,yend=r4.y,xend=r4.x[2])) + geom_segment(aes(x=r4.x[2],xend=r4.x[2],y=r4.verticals.start,yend=r4.verticals.stop)) + geom_segment(aes(x=r4.x[1],y=-r4.y,yend=-r4.y,xend=r4.x[2])) + geom_segment(aes(x=r4.x[2],xend=r4.x[2],y=-r4.verticals.start,yend=-r4.verticals.stop)) + geom_segment(aes(x=-r4.x[1],y=r4.y,yend=r4.y,xend=-r4.x[2])) + geom_segment(aes(x=-r4.x[2],xend=-r4.x[2],y=r4.verticals.start,yend=r4.verticals.stop)) + geom_segment(aes(x=-r4.x[1],y=-r4.y,yend=-r4.y,xend=-r4.x[2])) + geom_segment(aes(x=-r4.x[2],xend=-r4.x[2],y=-r4.verticals.start,yend=-r4.verticals.stop)) 

### add fifth round: add necessary horizontal bars and then
### vertical bars
empty.bracket <- empty.bracket + geom_segment(aes(x=r5.x[1],y=r5.y,yend=r5.y,xend=r5.x[2])) +  geom_segment(aes(x=r5.x[1],y=-r5.y,yend=-r5.y,xend=r5.x[2])) + geom_segment(aes(x=r5.x[2],y=-r5.y, yend=r5.y, xend=r5.x[2])) + geom_segment(aes(x=-r5.x[1],y=r5.y,yend=r5.y,xend=-r5.x[2])) + geom_segment(aes(x=-r5.x[1],y=-r5.y,yend=-r5.y,xend=-r5.x[2])) + geom_segment(aes(x=-r5.x[2],y=-r5.y,yend=r5.y,xend=-r5.x[2])) 

### due to symmetry, the 6th (and final round)
empty.bracket <- empty.bracket  + geom_segment(aes(x=r6.x[1],y=r6.y,xend=r6.x[2],yend=r6.y)) + geom_segment(aes(x=-r6.x[1],y=-r6.y,xend=-r6.x[2],yend=-r6.y))

### add winner location
empty.bracket <- empty.bracket + geom_segment(aes(x=mean(r6.x),xend=-mean(r6.x),y=0,yend=0))

### put some test labels on the bracket slots
Labels_og <- c("Duke",
               "Siena",
               "OSU",
               "TCU",
               "St John's",
               "Northern Iowa",
               "Kansas",
               "CA Baptist",
               "Louisville",
               "USF",
               "MSU",
               "NDSU",
               "UCLA",
               "UCF",
               "UConn",
               "Furman"
)
Labels <- Labels_og
vec <- best_bracket[round == 1 & grp %like% 'E', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])
vec <- best_bracket[round == 2 & grp %like% 'E', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])
vec <- best_bracket[round == 3 & grp %like% 'E', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])
vec <- best_bracket[round == 4 & grp %like% 'E', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])



TextFrame <- data.frame(X = c(rep(r1.x[1], 16), rep(r2.x[1], 8), rep(r3.x[1], 4), rep(r4.x[1], 2), rep(r5.x[1], 1)), Y = c(rev(r1.y), rev(r2.y), rev(r3.y), rev(r4.y), rev(r5.y)), LAB = Labels)
TextFrame <- transform(TextFrame, w = strwidth(LAB, 'inches') + 0.05, h = strheight(LAB, 'inches') + 0.5)

### display results
filled_bracket <- empty.bracket + geom_rect(data = TextFrame, aes(xmin = X, xmax = X + w, ymin = Y, ymax = Y + h),alpha=0) + geom_text(data=TextFrame,aes(x=X,y=Y,label=LAB),size=rel(3),hjust=-.05,vjust=-.2)

### put some test labels on the bracket slots
Labels_og <- c("Florida",
               "Lehigh/PV",
               "Clemson",
               "Iowa",
               "Vandy",
               "McNeese",
               "Nebraska",
               "Troy",
               "UNC",
               "VCU",
               "Illinois",
               "Penn",
               "St Mary's",
               "TAMU",
               "Houston",
               'Idaho'
)
Labels <- Labels_og
vec <- best_bracket[round == 1 & grp %like% 'S', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])
vec <- best_bracket[round == 2 & grp %like% 'S', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])
vec <- best_bracket[round == 3 & grp %like% 'S', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])
vec <- best_bracket[round == 4 & grp %like% 'S', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])

TextFrame <- data.frame(X = c(rep(r1.x[1], 16), rep(r2.x[1], 8), rep(r3.x[1], 4), rep(r4.x[1], 2), rep(r5.x[1], 1)), Y = -c(r1.y, r2.y, r3.y, r4.y, r5.y), LAB = Labels)
TextFrame <- transform(TextFrame, w = strwidth(LAB, 'inches') + 0.05, h = strheight(LAB, 'inches') + 0.5)

### display results
filled_bracket <- filled_bracket + geom_rect(data = TextFrame, aes(xmin = X, xmax = X + w, ymin = Y, ymax = Y + h),alpha=0) + geom_text(data=TextFrame,aes(x=X,y=Y,label=LAB),size=rel(3),hjust=-.05,vjust=-.2)


#Top Left

### put some test labels on the bracket slots
Labels_og <- c("Arizona",
               "Long Island",
               "Villanova",
               "Utah St",
               "Wisco",
               "High Point",
               "Arkansas",
               "Hawaii",
               "BYU",
               "Texas",
               "Gonzaga",
               "Kenn St",
               "Miami FL",
               "Missouri",
               "Purdue",
               "Queens"
               
)
Labels <- Labels_og
vec <- best_bracket[round == 1 & grp %like% 'W', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])
vec <- best_bracket[round == 2 & grp %like% 'W', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])
vec <- best_bracket[round == 3 & grp %like% 'W', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])
vec <- best_bracket[round == 4 & grp %like% 'W', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])

TextFrame <- data.frame(X = -c(rep(r1.x[2], 16), rep(r2.x[2], 8), rep(r3.x[2], 4), rep(r4.x[2], 2), rep(r5.x[2], 1)), Y = c(rev(r1.y), rev(r2.y), rev(r3.y), rev(r4.y), rev(r5.y)), LAB = Labels)
TextFrame <- transform(TextFrame, w = strwidth(LAB, 'inches') + 0.05, h = strheight(LAB, 'inches') + 0.5)

### display results
filled_bracket <- filled_bracket + geom_rect(data = TextFrame, aes(xmin = X, xmax = X + w, ymin = Y, ymax = Y + h),alpha=0) + geom_text(data=TextFrame,aes(x=X,y=Y,label=LAB),size=rel(3),hjust=0,vjust=-.2)

#Bottom Right

### put some test labels on the bracket slots
Labels_og <- c("Michigan",
               "Howard",
               "Georgia",
               "SLU",
               "TTU",
               "Akron",
               "Alabama",
               "Hofstra",
               "Tennessee",
               "SMU/Miami OH",
               "Virginia",
               "Wright St",
               "Kentucky",
               "Santa Clara",
               "Iowa St",
               'Tenn St'
               
               
)
Labels <- Labels_og
vec <- best_bracket[round == 1 & grp %like% 'M', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])
vec <- best_bracket[round == 2 & grp %like% 'M', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])
vec <- best_bracket[round == 3 & grp %like% 'M', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])
vec <- best_bracket[round == 4 & grp %like% 'M', Team]
Labels %<>% c(vec[order(match(vec, Labels_og))])

TextFrame <- data.frame(X = -c(rep(r1.x[2], 16), rep(r2.x[2], 8), rep(r3.x[2], 4), rep(r4.x[2], 2), rep(r5.x[2], 1)), Y = -c(r1.y, r2.y, r3.y, r4.y, r5.y), LAB = Labels)
TextFrame <- transform(TextFrame, w = strwidth(LAB, 'inches') + 0.05, h = strheight(LAB, 'inches') + 0.5)

### display results
filled_bracket <- filled_bracket + geom_rect(data = TextFrame, aes(xmin = X, xmax = X + w, ymin = Y, ymax = Y + h),alpha=0) + geom_text(data=TextFrame,aes(x=X,y=Y,label=LAB),size=rel(3),hjust=0,vjust=-.2)


#Left Semi
semi_1 <- best_bracket[round == 5 & grp == 1, Team]

TextFrame <- data.frame(X = r6.x[1], Y = r6.y, LAB = semi_1)
TextFrame <- transform(TextFrame, w = strwidth(LAB, 'inches') + 0.05, h = strheight(LAB, 'inches') + 0.5)

### display results
filled_bracket <- filled_bracket + geom_rect(data = TextFrame, aes(xmin = X, xmax = X + w, ymin = Y, ymax = Y + h),alpha=0) + geom_text(data=TextFrame,aes(x=X,y=Y,label=LAB),size=rel(3),hjust=0,vjust=-.2)

#Right Semi
semi_2 <- best_bracket[round == 5 & grp == 2, Team]

TextFrame <- data.frame(X = -r6.x[2], Y = -r6.y, LAB = semi_2)
TextFrame <- transform(TextFrame, w = strwidth(LAB, 'inches') + 0.05, h = strheight(LAB, 'inches') + 0.5)

### display results
filled_bracket <- filled_bracket + geom_rect(data = TextFrame, aes(xmin = X, xmax = X + w, ymin = Y, ymax = Y + h),alpha=0) + geom_text(data=TextFrame,aes(x=X,y=Y,label=LAB),size=rel(3),hjust=0,vjust=-.2)

#Final
champ <- best_bracket[round == 6, Team]

TextFrame <- data.frame(X = 0, Y = 0, LAB = champ)
TextFrame <- transform(TextFrame, w = strwidth(LAB, 'inches') + 0.05, h = strheight(LAB, 'inches') + 0.5)

### display results
filled_bracket <- filled_bracket + geom_rect(data = TextFrame, aes(xmin = X, xmax = X + w, ymin = Y, ymax = Y + h),alpha=0) + geom_text(data=TextFrame,aes(x=X,y=Y,label=LAB),size=rel(3),hjust=0.5,vjust=-.2)

filled_bracket

```

















